*Supplementary Material 1*

### 2022-06-22 ms/si.Rmd
Update MS
- add SI fig for t&s calibration points
- fix things according to input from ES, SRB

acc_table_long <- read_from_cache("acc_table_long", ftol_cache)
con_fossil_calibration_tips <- read_from_cache("con_fossil_calibration_tips", ftol_cache) # nolint
con_fossil_calibrations_for_treepl <- read_from_cache("con_fossil_calibrations_for_treepl", ftol_cache) # nolint
fossil_ferns_all <- read_from_cache("fossil_ferns_all", ftol_cache)
plastome_seqs_combined_filtered <- read_from_cache("plastome_seqs_combined_filtered", ftol_cache) # nolint
plastome_tree <- read_from_cache("plastome_tree", ftol_cache)
plastome_tree_rooted <- read_from_cache("plastome_tree_rooted", ftol_cache)
sanger_accessions_selection <- read_from_cache("sanger_accessions_selection", ftol_cache) # nolint
sanger_con_tree_dated <- read_from_cache("sanger_con_tree_dated", ftol_cache)
sanger_con_tree_rooted <- read_from_cache("sanger_con_tree_rooted", ftol_cache)
sanger_alignment_tbl <- read_from_cache("sanger_alignment_tbl", ftol_cache)
ts_fossil_calibration_tips <- read_from_cache("ts_fossil_calibration_tips", ftol_cache) # nolint
sanger_seqs_rogues_inspected <- read_from_cache(
  "sanger_seqs_rogues_inspected", ftol_cache
)

@@

```{r fossil-map-make}
# Make tibble with node number and label for ggtree
node_labs_tbl <-
  con_fossil_calibrations_for_treepl %>%
  transmute(
    fossil_label = str_remove_all(min, "min = "),
    node = map2_dbl(taxon_1, taxon_2, ~ape::getMRCA(sanger_con_tree_rooted, c(.x, .y))),
    calibration_type = case_when(
      !is.na(min) & is.na(max) ~ "minimum",
      !is.na(min) & !is.na(max) ~ "fixed",
      TRUE ~ NA_character_
    )
  ) %>%
  assert(not_na, calibration_type)

# Make plot
fossil_map_plot <- 
  ggtree(
    sanger_con_tree_rooted,
    branch.length = "none", size = 0.1, color = "grey30") %<+% node_labs_tbl +
  # Add node points
  geom_nodepoint(
    aes(color = calibration_type), size = 0.6) +
  scale_color_manual(
    "Calibration type",
    values = c(
      minimum = palette_okabe_ito("vermillion"), 
      fixed = palette_okabe_ito("skyblue")),
    na.value = "transparent"
  ) +
  # Add node labels
  geom_text(aes(label = fossil_label), hjust = 0, size = 1.0, color = "grey20") +
  # Add tip labels
  geom_tiplab(aes(label = label), size = 0.5, color = "grey30") +
  theme(legend.position = "bottom")
```

@@

```{r backbone-full-save, eval = params$doc_type == "doc"}
ggsave(
  plot = bb_full_plot,
  file = (result_file(s_figure("backbone_full"), "pdf")),
  height = 20, width = 8, units = "in",
  limitsize = FALSE)
```

@@

@@

>>>>

acc_table_long <- read_from_cache("acc_table_long", ftol_cache)
con_fossil_calibration_tips <- read_from_cache("con_fossil_calibration_tips", ftol_cache) # nolint
con_fossil_calibrations_for_treepl <- read_from_cache("con_fossil_calibrations_for_treepl", ftol_cache) # nolint
fossil_ferns_all <- read_from_cache("fossil_ferns_all", ftol_cache)
plastome_seqs_combined_filtered <- read_from_cache("plastome_seqs_combined_filtered", ftol_cache) # nolint
plastome_tree <- read_from_cache("plastome_tree", ftol_cache)
plastome_tree_rooted <- read_from_cache("plastome_tree_rooted", ftol_cache)
sanger_accessions_selection <- read_from_cache("sanger_accessions_selection", ftol_cache) # nolint
sanger_con_tree_dated <- read_from_cache("sanger_con_tree_dated", ftol_cache)
sanger_con_tree_rooted <- read_from_cache("sanger_con_tree_rooted", ftol_cache)
sanger_con_tree_rooted_pruned <- read_from_cache(
  "sanger_con_tree_rooted_pruned", ftol_cache)
sanger_alignment_tbl <- read_from_cache("sanger_alignment_tbl", ftol_cache)
ts_fossil_calibration_tips <- read_from_cache("ts_fossil_calibration_tips", ftol_cache) # nolint
sanger_seqs_rogues_inspected <- read_from_cache(
  "sanger_seqs_rogues_inspected", ftol_cache
)
ts_fossil_calibrations_for_treepl <- read_from_cache(
  "ts_fossil_calibrations_for_treepl", ftol_cache)

@@

```{r fossil-map-make}
# Make tibble with node number and label for ggtree
node_labs_tbl <-
  con_fossil_calibrations_for_treepl %>%
  transmute(
    fossil_label = str_remove_all(min, "min = "),
    node = map2_dbl(
      taxon_1, taxon_2,
      ~ape::getMRCA(sanger_con_tree_rooted_pruned, c(.x, .y))),
    calibration_type = case_when(
      !is.na(min) & is.na(max) ~ "minimum",
      !is.na(min) & !is.na(max) ~ "fixed",
      TRUE ~ NA_character_
    )
  ) %>%
  assert(not_na, calibration_type)

# Make plot
fossil_map_plot <-
  ggtree(
    sanger_con_tree_rooted_pruned,
    branch.length = "none", size = 0.1, color = "grey30") %<+% node_labs_tbl +
  # Add node points
  geom_nodepoint(
    aes(color = calibration_type), size = 0.6) +
  scale_color_manual(
    "Calibration type",
    values = c(
      minimum = palette_okabe_ito("vermillion"),
      fixed = palette_okabe_ito("skyblue")),
    na.value = "transparent"
  ) +
  # Add node labels
  geom_text(
    aes(label = fossil_label), hjust = 0, size = 1.0, color = "grey20") +
  # Add tip labels
  geom_tiplab(aes(label = label), size = 0.5, color = "grey30") +
  theme(legend.position = "bottom")
```

@@

@@

```{r backbone-full-save, eval = params$doc_type == "doc"}
ggsave(
  plot = bb_full_plot,
  file = (result_file(s_figure("backbone_full"), "pdf")),
  height = 20, width = 10, units = "in",
  limitsize = FALSE)
```

@@

```{r ts-fossil-map-make}
# Make tibble with node number and label for ggtree
ts_node_labs_tbl <-
  ts_fossil_calibrations_for_treepl %>%
  transmute(
    fossil_label = str_remove_all(min, "min = "),
    node = map2_dbl(
      taxon_1, taxon_2,
      ~ape::getMRCA(sanger_con_tree_rooted_pruned, c(.x, .y))),
    calibration_type = case_when(
      !is.na(min) & is.na(max) ~ "minimum",
      !is.na(min) & !is.na(max) ~ "fixed",
      TRUE ~ NA_character_
    )
  ) %>%
  assert(not_na, calibration_type)

# Make plot
fossil_map_plot <-
  ggtree(
    sanger_con_tree_rooted_pruned,
    branch.length = "none",
    size = 0.1, color = "grey30") %<+% ts_node_labs_tbl +
  # Add node points
  geom_nodepoint(
    aes(color = calibration_type), size = 0.6) +
  scale_color_manual(
    "Calibration type",
    values = c(
      minimum = palette_okabe_ito("vermillion"),
      fixed = palette_okabe_ito("skyblue")),
    na.value = "transparent"
  ) +
  # Add node labels
  geom_text(
    aes(label = fossil_label), hjust = 0, size = 1.0, color = "grey20") +
  # Add tip labels
  geom_tiplab(aes(label = label), size = 0.5, color = "grey30") +
  theme(legend.position = "bottom")
```

```{r ts-fossil-map-save, eval = params$doc_type == "doc"}
ggsave(
  plot = fossil_map_plot,
  file = (result_file(s_figure("ts_fossil_map"), "pdf")),
  height = 60, width = 8, units = "in",
  limitsize = FALSE)
```

**`r s_figure("ts_fossil_map")`**.
Consensus phylogeny (Sanger dataset) with node labels indicating placement of fossil constraints of @Testo2016a.
Number for each constraint is age in Ma.
